---
title: "Polarity_score_analysis_withOpinionFlag"
output:
  pdf_document: default
  html_document: default
date: "2024-04-28"
---

## R Markdown

```{r}
library(ggplot2)
library(dplyr)

data <- read.csv("/Users/winni/Desktop/Comp\ 560/polarity_scores_fr_no_dupes.csv")

data$Clean.Link <- gsub(".com", "", data$`Clean.Link`, fixed = TRUE)
data$Clean.Link<- as.factor(data$Clean.Link)
data <- data %>%
  rename(News_Org = Clean.Link)

```


```{r}
data_cleaned <- data[data$Opinion != "", ]
unique(data_cleaned$Opinion)
```


opinion_articles <- subset(data, Opinion == "True")
non_opinion_articles <- subset(data, Opinion == "False")

head(non_opinion_articles)
head(opinion_articles)

```{r}
t_test <- t.test(data_cleaned$Whole.Article.Compound.Polarity ~ data_cleaned$Opinion)
cat("T-test p-value:", t_test$p.value, "\n")
```
```{r}
grouped_data <- data %>%
  group_by(News_Org) %>%
  summarise(
    Mean_Compound_Polarity = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Mean_Pos_Polarity = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Mean_Neu_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Mean_Neg_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE)
  )
print(grouped_data)
```

```{r}
#Whole.Article.Compound.Polarity per news org
#opinion
opinion_grouped_data <- opinion_articles %>%
  group_by(News_Org) %>%
  summarise(
    Mean_Compound_Polarity = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Compound.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Count = n()
  )
print(opinion_grouped_data)

ggplot(opinion_articles, aes(x = News_Org, y = Whole.Article.Compound.Polarity, fill = News_Org)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Compound Polarity by News Organization with Opinion",
       x = "News Organization",
       y = "Whole Article Compound Polarity")

ggplot(opinion_grouped_data, aes(x = News_Org, y = Mean_Compound_Polarity, fill = News_Org)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Compound Polarity by News Organization with Opinion",
       x = "News Organization",
       y = "Mean Polarity")

t_test <- t.test(data$Whole.Article.Compound.Polarity ~ data$Opinion)
cat("T-test p-value:", t_test$p.value, "\n")
```

```{r}

#non-opinion

non_opinion_grouped_data <- non_opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Compound.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Count = n()
  )
print(non_opinion_grouped_data)

ggplot(non_opinion_articles, aes(x = Clean.Link, y = Whole.Article.Compound.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Compound Polarity by News Organization with non-opinion",
       x = "News Organization",
       y = "Whole Article Compound Polarity")

ggplot(opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Compound Polarity by News Organization with non-opinion",
       x = "News Organization",
       y = "Mean Polarity")
```
```{r}
head(opinion_articles)
library(lubridate)

# Convert Publish_Date to Date format
opinion_articles$Publish.Date <- ymd_hms(opinion_articles$Publish.Date)

# Plot the trend with formatted dates
ggplot(opinion_articles, aes(x = as.Date(Publish.Date), y = Whole.Article.Compound.Polarity)) +  # Convert to Date format
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  labs(title = "Trend of Compound Polarity Scores Over Time",
       x = "Publication Date", y = "Compound Polarity") +
  scale_x_date(date_labels = "%Y-%m-%d")  # Format x-axis dates


correlation_matrix <- cor(data[, c("Whole.Article.Compound.Polarity", "Sentence.Count")], use = "complete.obs")
print(correlation_matrix)

# Visualize correlation matrix
corrplot(correlation_matrix, method = "circle", type = "upper")

# 4. Qualitative Analysis
# Select subset of articles with extreme polarity scores for qualitative analysis
extreme_articles <- data[abs(data$Compound_Polarity) > 0.8, ]

```

```{r}
#Whole.Article.Pos.Polarity per news org
#opinion
opinion_grouped_data <- opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Pos.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Count = n()
  )
print(opinion_grouped_data)

ggplot(opinion_articles, aes(x = Clean.Link, y = Whole.Article.Pos.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Pos Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Whole Article Pos Polarity")

ggplot(opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Pos Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Mean Polarity")

#non-opinion
non_opinion_grouped_data <- non_opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Pos.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Count = n()
  )
print(non_opinion_grouped_data)

ggplot(non_opinion_articles, aes(x = Clean.Link, y = Whole.Article.Pos.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Pos Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Whole Article Pos Polarity")

ggplot(opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Pos Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Mean Polarity")
```


```{r}
#Whole.Article.Neg.Polarity per news org
#opinion
opinion_grouped_data <- opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Neg.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Count = n()
  )
print(opinion_grouped_data)

ggplot(opinion_articles, aes(x = Clean.Link, y = Whole.Article.Neg.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Neg Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Whole Article Neg Polarity")

ggplot(opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Neg Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Mean Polarity")

#non-opinion
non_opinion_grouped_data <- non_opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Neg.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Count = n()
  )
print(non_opinion_grouped_data)

ggplot(non_opinion_articles, aes(x = Clean.Link, y = Whole.Article.Neg.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Neg Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Whole Article Neg Polarity")

ggplot(non_opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Neg Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Mean Polarity")
```

```{r}
#Whole.Article.Neu.Polarity per news org
#opinion
opinion_grouped_data <- opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Neu.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Count = n()
  )
print(opinion_grouped_data)

ggplot(opinion_articles, aes(x = Clean.Link, y = Whole.Article.Neu.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Neu Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Whole Article Neu Polarity")

ggplot(opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Neu Polarity by News Organization with opinion",
       x = "News Organization",
       y = "Mean Polarity")

#non_opinion
non_opinion_grouped_data <- non_opinion_articles %>%
  group_by(Clean.Link) %>%
  summarise(
    Mean_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Median_Polarity = median(Whole.Article.Neu.Polarity, na.rm = TRUE),
    SD_Polarity = sd(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Count = n()
  )
print(non_opinion_grouped_data)

ggplot(non_opinion_articles, aes(x = Clean.Link, y = Whole.Article.Neu.Polarity, fill = Clean.Link)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Whole Article Neu Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Whole Article Neu Polarity")

ggplot(non_opinion_grouped_data, aes(x = Clean.Link, y = Mean_Polarity, fill = Clean.Link)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Mean Whole Article Neu Polarity by News Organization with non_opinion",
       x = "News Organization",
       y = "Mean Polarity")
```

```{r}
#Whole.Article.Compound.Polarity per issue
#opinion
opinion_articles <- opinion_articles %>%
  mutate(Issue = gsub("_.*", "", Category),
         News_Org = gsub(".*_", "", Category))

average_polarity_per_issue_opinion <- opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Compound.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_opinion)

ggplot(average_polarity_per_issue_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Compound Polarity per Issue with opinion",
       x = "Issue",
       y = "Average Compound Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


#non_opinion
non_opinion_articles <- non_opinion_articles %>%
  mutate(Issue = gsub("_.*", "", Category),
         News_Org = gsub(".*_", "", Category))

average_polarity_per_issue_non_opinion <- non_opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Compound.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Compound.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_non_opinion)

ggplot(average_polarity_per_issue_non_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Compound Polarity per Issue with non_opinion",
       x = "Issue",
       y = "Average Compound Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
#Whole.Article.Pos.Polarity per issue
#opinion
average_polarity_per_issue_opinion <- opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Pos.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_opinion)

ggplot(average_polarity_per_issue_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Pos Polarity per Issue with opinion",
       x = "Issue",
       y = "Average Pos Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


#non_opinion
average_polarity_per_issue_non_opinion <- non_opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Pos.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Pos.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_non_opinion)

ggplot(average_polarity_per_issue_non_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Pos Polarity per Issue with non_opinion",
       x = "Issue",
       y = "Average Pos Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
#Whole.Article.Neg.Polarity per issue
#opinion
average_polarity_per_issue_opinion <- opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Neg.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Neg.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_opinion)

ggplot(average_polarity_per_issue_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Neg Polarity per Issue with opinion",
       x = "Issue",
       y = "Average Neg Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#non_opinion
average_polarity_per_issue_non_opinion <- non_opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Neg.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Neg.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Neg.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_non_opinion)

ggplot(average_polarity_per_issue_non_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Neg Polarity per Issue with non_opinion",
       x = "Issue",
       y = "Average Neg Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
#Whole.Article.Neu.Polarity per issue
#opinion
average_polarity_per_issue_opinion <- opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Neu.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_opinion)

ggplot(average_polarity_per_issue_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Neu Polarity per Issue with opinion",
       x = "Issue",
       y = "Average Neu Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#non_opinion
average_polarity_per_issue_non_opinion <- non_opinion_articles %>%
  group_by(Issue) %>%
  summarise(
    Avg_Compound_Polarity = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
    SD_Compound_Polarity = sd(Whole.Article.Neu.Polarity, na.rm = TRUE),
    Median_Compound_Polarity = median(Whole.Article.Neu.Polarity, na.rm = TRUE)
  )

print(average_polarity_per_issue_non_opinion)

ggplot(average_polarity_per_issue_non_opinion, aes(x = Issue, y = Avg_Compound_Polarity, fill = Issue)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Whole Article Neu Polarity per Issue with non_opinion",
       x = "Issue",
       y = "Average Neu Polarity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r}
#opinion
# Calculate correlation between whole article compound polarity and sentence count
cor_compound_sentence_opinion <- cor(opinion_articles$`Whole.Article.Compound.Polarity`, opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article neg polarity and sentence count
cor_neg_sentence_opinion <- cor(opinion_articles$`Whole.Article.Neg.Polarity`, opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article pos polarity and sentence count
cor_pos_sentence_opinion <- cor(opinion_articles$`Whole.Article.Pos.Polarity`, opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article neu polarity and sentence count
cor_neu_sentence_opinion <- cor(opinion_articles$`Whole.Article.Neu.Polarity`, opinion_articles$`Sentence.Count`, use = "complete.obs")

#non_opinion
# Calculate correlation between whole article compound polarity and sentence count
cor_compound_sentence_non_opinion <- cor(non_opinion_articles$`Whole.Article.Compound.Polarity`, non_opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article neg polarity and sentence count
cor_neg_sentence_non_opinion <- cor(non_opinion_articles$`Whole.Article.Neg.Polarity`, non_opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article pos polarity and sentence count
cor_pos_sentence_non_opinion <- cor(non_opinion_articles$`Whole.Article.Pos.Polarity`, non_opinion_articles$`Sentence.Count`, use = "complete.obs")

# Calculate correlation between whole article neu polarity and sentence count
cor_neu_sentence_non_opinion <- cor(non_opinion_articles$`Whole.Article.Neu.Polarity`, non_opinion_articles$`Sentence.Count`, use = "complete.obs")

# Print the correlations
print(paste("Correlation of Whole Article Compound Polarity and Sentence Count with opinion:", cor_compound_sentence_opinion))
print(paste("Correlation of Whole Article Neg Polarity and Sentence Count with opinion:", cor_neg_sentence_opinion))
print(paste("Correlation of Whole Article Pos Polarity and Sentence Count with opinion:", cor_pos_sentence_opinion))
print(paste("Correlation of Whole Article Neu Polarity and Sentence Count with opinion:", cor_neu_sentence_opinion))

print(paste("Correlation of Whole Article Compound Polarity and Sentence Count with non_opinion:", cor_compound_sentence_non_opinion))
print(paste("Correlation of Whole Article Neg Polarity and Sentence Count with non_opinion:", cor_neg_sentence_non_opinion))
print(paste("Correlation of Whole Article Pos Polarity and Sentence Count with non_opinion:", cor_pos_sentence_non_opinion))
print(paste("Correlation of Whole Article Neu Polarity and Sentence Count with non_opinion:", cor_neu_sentence_non_opinion))

```
```{r}
#Correlation matrix of Polarity and Sentence Count
#opinion
polarity_sentence_data_opinion <- opinion_articles[,c('Whole.Article.Compound.Polarity', 
                                  'Whole.Article.Neg.Polarity', 
                                  'Whole.Article.Pos.Polarity', 
                                  'Whole.Article.Neu.Polarity', 
                                  'Sentence.Count')]

cor_matrix_opinion <- cor(polarity_sentence_data_opinion, use = "complete.obs")
print(cor_matrix_opinion)

#non_opinion
polarity_sentence_data_non_opinion <- non_opinion_articles[,c('Whole.Article.Compound.Polarity', 
                                  'Whole.Article.Neg.Polarity', 
                                  'Whole.Article.Pos.Polarity', 
                                  'Whole.Article.Neu.Polarity', 
                                  'Sentence.Count')]

cor_matrix_non_opinion <- cor(polarity_sentence_data_non_opinion, use = "complete.obs")
print(cor_matrix_non_opinion)
library(corrplot)
corrplot(cor_matrix_opinion, method = "circle")
corrplot(cor_matrix_non_opinion, method = "circle")
```

```{r}
library(patchwork)
# Perform regression analysis for non_opinion_articles dataset
reg_compound_non_opinion <- lm(`Whole.Article.Compound.Polarity` ~ `Sentence.Count`, data = non_opinion_articles)
reg_neg_non_opinion <- lm(`Whole.Article.Neg.Polarity` ~ `Sentence.Count`, data = non_opinion_articles)
reg_pos_non_opinion <- lm(`Whole.Article.Pos.Polarity` ~ `Sentence.Count`, data = non_opinion_articles)
reg_neu_non_opinion <- lm(`Whole.Article.Neu.Polarity` ~ `Sentence.Count`, data = non_opinion_articles)

# Perform regression analysis for opinion_articles dataset
reg_compound_opinion <- lm(`Whole.Article.Compound.Polarity` ~ `Sentence.Count`, data = opinion_articles)
reg_neg_opinion <- lm(`Whole.Article.Neg.Polarity` ~ `Sentence.Count`, data = opinion_articles)
reg_pos_opinion <- lm(`Whole.Article.Pos.Polarity` ~ `Sentence.Count`, data = opinion_articles)
reg_neu_opinion <- lm(`Whole.Article.Neu.Polarity` ~ `Sentence.Count`, data = opinion_articles)

# Compound
plot_non_opinion <- ggplot(non_opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Compound.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Non-opinion",
       x = "Sentence Count",
       y = "Whole Article Compound Polarity")

plot_opinion <- ggplot(opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Compound.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Opinion",
       x = "Sentence Count",
       y = "Whole Article Compound Polarity")

plot_non_opinion + plot_opinion

#Neg
plot_non_opinion <- ggplot(non_opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Neg.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Non-opinion",
       x = "Sentence Count",
       y = "Whole Article Neg Polarity")

plot_opinion <- ggplot(opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Neg.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Opinion",
       x = "Sentence Count",
       y = "Whole Article Neg Polarity")

plot_non_opinion + plot_opinion

#Neu
plot_non_opinion <- ggplot(non_opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Neu.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Non-opinion",
       x = "Sentence Count",
       y = "Whole Article Neu Polarity")

plot_opinion <- ggplot(opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Neu.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Opinion",
       x = "Sentence Count",
       y = "Whole Article Neu Polarity")

plot_non_opinion + plot_opinion

#Pos
plot_non_opinion <- ggplot(non_opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Pos.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Non-opinion",
       x = "Sentence Count",
       y = "Whole Article Pos Polarity")

plot_opinion <- ggplot(opinion_articles, aes(x = `Sentence.Count`, y = `Whole.Article.Pos.Polarity`)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Opinion",
       x = "Sentence Count",
       y = "Whole Article Pos Polarity")

plot_non_opinion + plot_opinion

```

```{r}
Issue_News_Org_Opinion <- opinion_articles %>%
  group_by(Issue, Clean.Link) %>%
  summarise(Avg_Compound_Polarity_Opinion = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
            Avg_Pos_Polarity_Opinion = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
            Avg_Neu_Polarity_Opinion = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
            Avg_Neg_Polarity_Opinion = mean(Whole.Article.Neg.Polarity, na.rm = TRUE)
            )
print(Issue_News_Org_Opinion)

Issue_News_Org_Non_Opinion <- non_opinion_articles %>%
  group_by(Issue, Clean.Link) %>%
  summarise(Avg_Compound_Polarity_nonOpinion = mean(Whole.Article.Compound.Polarity, na.rm = TRUE),
            Avg_Pos_Polarity_Opinion = mean(Whole.Article.Pos.Polarity, na.rm = TRUE),
            Avg_Neu_Polarity_Opinion = mean(Whole.Article.Neu.Polarity, na.rm = TRUE),
            Avg_Neg_Polarity_Opinion = mean(Whole.Article.Neg.Polarity, na.rm = TRUE)
            )
print(Issue_News_Org_Non_Opinion)


ggplot(Issue_News_Org_Opinion, aes(x = Issue, y = Avg_Compound_Polarity_Opinion, color = Clean.Link)) +
  geom_point() +
  labs(title = "Average Compound Polarity by Issue and News Organization (Opinion)",
       x = "Issue",
       y = "Average Compound Polarity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(Issue_News_Org_Non_Opinion, aes(x = Issue, y = Avg_Compound_Polarity_nonOpinion, color = Clean.Link)) +
  geom_point() +
  labs(title = "Average Compound Polarity by Issue and News Organization (Non Opinion)",
       x = "Issue",
       y = "Average Compound Polarity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```